Supplementary Material: Constructing Statistical Deformable Models with Shape Flow

### 2015-11-10 supplementary.tex
Updates from ShareLaTeX

\begin{figure}[!t]
\centering
\includegraphics[width=0.5\textwidth]{supports/Fittings/fittings}
\caption{Result of fitting dAAMs on ears (first two rows) and faces (last two rows). A dense grid visualisation is used.}
\label{fig:fr}
\end{figure}

@@

\begin{figure}[!b]
    \centering
    % \vspace*{-0.1in}
    \begin{subfigure}[b]{0.43\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/sr_ear}
        %\caption{dAAMs dense shape reconstruction}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.43\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/sr_face}
        %\caption{AAMs dense shape reconstruction}
    \end{subfigure}
    \caption{Dense shape reconstruction errors for ears and faces. Top: results of reconstruction on ears, bottom: results of reconstruction on faces. The normalised point-to-point error is used an evaluation measure.}
    \label{fig:rc_face}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{0.43\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/var_ratio}
        %\caption{dAAMs vs AAMs Variance Ratio}
    \end{subfigure}
    \begin{subfigure}[b]{0.43\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/cumu_var_ratio}
        %\caption{dAAMs vs AAMs Cumulative Variance Ratio}
    \end{subfigure}
    \caption{Variance explained by each principal component, for both dAAM and AAM models. Top: variance explained by each principal component. Bottom: cumulative plot of the variance explained as a function of the principal components.}
    \label{fig:compact}
\end{figure}

@@

\begin{figure*}[!t]
\centering
\includegraphics[width=\textwidth]{supports/Models/models}
\caption{Principal components of dAAMs built on ears (top) and faces (bottom). The mean (middle columns) as well as the first five principal components are visualised for both shape (left) and appearance (right). $\pm 3$ times the variance of the corresponding component is used in each case.}
\label{fig:pcamodel}
\end{figure*}

@@

\begin{figure}[!b]
    \centering
    %\vspace*{-0.2in}
    \includegraphics[width=0.5\textwidth]{resources/Fig_Draw/draw}
    \caption{Synthesizing face images from caricature sketches. First column: caricature sketches. Second column: arbitrary chosen face images. Third and last column: sketch-based warping of images based on AAMs (third column) and dAAMs (last column).}
    \label{fig:draw}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{0.15\textwidth}
            \includegraphics[height=\textwidth]{supports/Segmentation_Measure/ear}
        %\caption{Ear Initial Bounding Box}
    \end{subfigure}
    \begin{subfigure}[b]{0.15\textwidth}
            \includegraphics[height=\textwidth]{supports/Segmentation_Measure/bottle}
        %\caption{Bottle Initial Bounding Box}
    \end{subfigure}
    \begin{subfigure}[b]{0.15\textwidth}
            \includegraphics[height=\textwidth]{supports/Segmentation_Measure/body}
        %\caption{Body Initial Bounding Box}
    \end{subfigure}
    \caption{Examples of fitting initialisations used for the segmentation experiment. These are created by random perturbation of the ground-truth bounding box.}
    \label{fig:seg_init}
\end{figure}

>>>>

\begin{figure}[!t]
\centering
\includegraphics[width=0.5\textwidth]{Supplementory_Meterial/Fittings/fittings}
\caption{Result of fitting dAAMs on ears (first two rows) and faces (last two rows). A dense grid visualisation is used.}
\label{fig:fr}
\end{figure}

@@

\begin{figure}[!b]
    \centering
    % \vspace*{-0.1in}
    \begin{subfigure}[b]{0.43\textwidth}
            \includegraphics[width=\textwidth]{Supplementory_Meterial/Model_Analysis/sr_ear}
        %\caption{dAAMs dense shape reconstruction}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.43\textwidth}
            \includegraphics[width=\textwidth]{Supplementory_Meterial/Model_Analysis/sr_face}
        %\caption{AAMs dense shape reconstruction}
    \end{subfigure}
    \caption{Dense shape reconstruction errors for ears and faces. Top: results of reconstruction on ears, bottom: results of reconstruction on faces. The normalised point-to-point error is used an evaluation measure.}
    \label{fig:rc_face}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{0.43\textwidth}
            \includegraphics[width=\textwidth]{Supplementory_Meterial/Model_Analysis/var_ratio}
        %\caption{dAAMs vs AAMs Variance Ratio}
    \end{subfigure}
    \begin{subfigure}[b]{0.43\textwidth}
            \includegraphics[width=\textwidth]{Supplementory_Meterial/Model_Analysis/cumu_var_ratio}
        %\caption{dAAMs vs AAMs Cumulative Variance Ratio}
    \end{subfigure}
    \caption{Variance explained by each principal component, for both dAAM and AAM models. Top: variance explained by each principal component. Bottom: cumulative plot of the variance explained as a function of the principal components.}
    \label{fig:compact}
\end{figure}

@@

\begin{figure*}[!t]
\centering
\includegraphics[width=\textwidth]{Supplementory_Meterial/Models/models}
\caption{Principal components of dAAMs built on ears (top) and faces (bottom). The mean (middle columns) as well as the first five principal components are visualised for both shape (left) and appearance (right). $\pm 3$ times the variance of the corresponding component is used in each case.}
\label{fig:pcamodel}
\end{figure*}

@@

\begin{figure}[!b]
    \centering
    %\vspace*{-0.2in}
    \includegraphics[width=0.5\textwidth]{Supplementory_Meterial/Fig_Draw/draw}
    \caption{Synthesizing face images from caricature sketches. First column: caricature sketches. Second column: arbitrary chosen face images. Third and last column: sketch-based warping of images based on AAMs (third column) and dAAMs (last column).}
    \label{fig:draw}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{0.15\textwidth}
            \includegraphics[height=\textwidth]{Supplementory_Meterial/Segmentation_Measure/ear}
        %\caption{Ear Initial Bounding Box}
    \end{subfigure}
    \begin{subfigure}[b]{0.15\textwidth}
            \includegraphics[height=\textwidth]{Supplementory_Meterial/Segmentation_Measure/bottle}
        %\caption{Bottle Initial Bounding Box}
    \end{subfigure}
    \begin{subfigure}[b]{0.15\textwidth}
            \includegraphics[height=\textwidth]{Supplementory_Meterial/Segmentation_Measure/body}
        %\caption{Body Initial Bounding Box}
    \end{subfigure}
    \caption{Examples of fitting initialisations used for the segmentation experiment. These are created by random perturbation of the ground-truth bounding box.}
    \label{fig:seg_init}
\end{figure}
